Clustering in a hyperbolic model of complex networks.

### 2019-05-01 concentration_argument.tex
processed most of Nikolaos comments on sections 5-7

Here we show that if we integrate with respect to a function $\hat{\rho}_n(y,k_n) = \Prob{\Po(\mu_n(y)) = k_n}$ then we may restrict integration with respect to the \emph{height} $y$ to an interval on which $\mu_n(y) = \bigT{k_n}$. We will refer to such a result as a \emph{concentration of heights} result. In addition, if $\mu_n(y)$ is equivalent to $\mu(y)$ on this interval, then we may replace $\hat{\rho}_n(y,k_n)$ in the integral with $\rho(y,k_n) = \Prob{\Po(\mu(y)) = k_n}$ (the degree distribution of the typical point in $\Ginf$).

@@

\begin{lemma}\label{lem:concentration_argument}
Let $\alpha > \frac{1}{2}$, $\nu > 0$, $(k_n)_{n \ge 1}$ be any positive sequence such that $k_n \to \infty$ and $k_n = \smallO{n}$ and let $\ell_n = k_n(1 + \epsilon_n)$, with $\epsilon_n \to 0$. In addition, define for any constant $C > 0$,
\[
	\lambda_n^\pm = (\ell_n \pm C \sqrt{\ell_n \log(\ell_n)}) \wedge \xi, 
	\quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi}\right).
\] 
Then the following holds.
\begin{enumerate}
\item For any continuous function $h : \R_+ \rightarrow  \R$, such that $h(y) = \bigO{e^{\beta y}}$ as $y \to \infty$ for some $\beta < \alpha$, 
\begin{equation}\label{eq:error_bound_int_rho_not_K}
	\int_{\R_+ \setminus (a_n^-, a_n^+)} \rho(y,k_n) h(y) \alpha e^{-\alpha y} \dd y
	= \bigO{k_n^{-(1+C^2)/2}},
\end{equation}
as $n \to \infty$.
\item If in addition, $h(a_n) \sim h(b_n)$ whenever $a_n \sim b_n$, as $n \to \infty$. Then,
\begin{equation}\label{eq:concentration_h_rho}
	\int_0^\infty h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y \sim  
		2\alpha \xi^{2\alpha} h(2\log(k_n/\xi)) k_n^{-(2\alpha + 1)},
\end{equation}
as $n \to \infty$.
\end{enumerate}
\end{lemma}

@@

\paragraph{Proof of the first statement.}
Recall (see proof of Proposition~\ref{prop:asymp}) that $\rho(y,k_n)$, as a function of $y$, is strictly increasing on $[0,a_n^-]$ and strictly decreasing on $[a_n^+,\infty)$. Therefore, by our assumption on $h(y)$,
\begin{align*}
	&\hspace{-20pt}\int_{\R_+ \setminus (a_n^-, a_n^+)} h(y) \rho(y,k_n) 
		\alpha e^{-\alpha y} \dd y\\
    &= \bigO{1} \int_0^{a_n^-} e^{\beta y} \rho(y,k_n) \alpha e^{-\alpha y} \dd y 
    	+ \bigO{1}\int_{a_n^+}^{\infty} e^{\beta y} \rho(y,k_n) \alpha e^{-\alpha y} \dd y \\
    &= \bigO{1} \int_0^{a_n^-} \rho(y,k_n) e^{-(\alpha-\beta) y} \dd y 
   		+ \bigO{1} \int_{a_n^+}^{\infty} \rho(y,k_n) e^{-(\alpha-\beta) y} \dd y\\
   	&\le \bigO{1}\rho(a_n^-,k_n)\int_0^{a_n^-} e^{-(\alpha-\beta) y} \, \dd y
   		+ \bigO{1} \rho(a_n^+,k_n) \int_{a_n^+}^{\infty} e^{-(\alpha-\beta) y} \, \dd y.
\end{align*}
Since $\alpha - \beta > 0$, we conclude that
\begin{equation}\label{eq:concentration_lemma_integral_bound}
	\int_{\R_+ \setminus (a_n^-, a_n^+)} h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y
	= \bigO{1} \left(\rho(a_n^-,k_n) + \rho(a_n^+,k_n)\right) 
\end{equation}

We shall now bound the terms $\rho(a_n^\pm,k_n)$, starting with $\rho(a_n^+,k_n)$.  Using Stirling's approximation $k! \sim \sqrt{2\pi} k^{k + 1/2} e^{-k}$ as $k \to \infty$ we write
\begin{align*}
	\rho(a_n^+,k_n) &= \frac{\mu(a_n^+)^{k_n}}{k_n!} e^{-\mu(a_n^+)} \\
	&\sim (2\pi)^{-1/2} k_n^{-1/2} \left(\frac{\mu(a_n^+)}{k_n}\right)^{k_n} e^{-(\mu(a_n^+) - k_n)}\\
	&= (2\pi)^{-1/2} k_n^{-1/2} 
		e^{-k_n\left(\frac{\mu(a_n^+)}{k_n} - 1 - \log\left(\frac{\mu(a_n^+)}{k_n}\right)\right)}.
\end{align*}

@@

\paragraph{Proof of the second statement.} By the mean value theorem for definite integrals, there exists a $c_n \in (a_n^-, a_n^+)$ such that
\[
	\int_{a_n^-}^{a_n^+} h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y
	= h(c_n) \int_{a_n^+}^{a_n^+} \rho(y,k_n) \alpha e^{-\alpha y} \dd y.
\]
Since $\int_0^\infty \rho(y,k_n) \alpha e^{-\alpha y} \dd y = \bigT{k_n^{-(2\alpha + 1)}}$, taking any $C > \sqrt{4\alpha + 1}$, \eqref{eq:error_bound_int_rho_not_K} implies that
\[
	\int_{a_n^+}^{a_n^+} \rho(y,k_n) \alpha e^{-\alpha y} \dd y
	= (1 + \smallO{1})\int_0^\infty \rho(y,k_n) \alpha e^{-\alpha y} \dd y,
\]
from which we conclude that (see~\eqref{eq:degree_distribution_P_asymptotics}),
\[
	\int_{a_n^+}^{a_n^+} \rho(y,k_n) \alpha e^{-\alpha y} \dd y = (1 + \smallO{1}) 2\alpha \xi^{2\alpha} k_n^{-(2\alpha + 1)},
\]
as $n \to \infty$. Finally, since $c_n \in (a_n^-, a_n^+)$ it follows that
\[
	\left|\frac{c_n}{2\log(k_n/\xi)} - 1\right| \le 2 C \sqrt{\frac{\log(k_n)}{k_n}}, 
\]
so that $c_n \sim k_n$. Therefore, by assumption on $h$ 
\[
	\int_{a_n^-}^{a_n^+} h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y
	\sim h(c_n) 2\alpha \xi^{2\alpha} k_n^{-(2\alpha + 1)} 
	\sim 2\alpha \xi^{2\alpha} h(2\log(k_n/\xi)) k_n^{-(2\alpha + 1),}
\]
as $n \to \infty$.
\end{proof}

@@

\begin{corollary}\label{cor:concentration_of_heights_asymptotics}
Let $h : \R_+ \to \R$ be any continuous function such that for some $\beta < \alpha$, $h(y) = \bigO{e^{\beta y}}$ as $y \to \infty$ and $h(a_n) \sim h(b_n)$ whenever $a_n \sim b_n$. Then for any other continuous function $g: \R_+ \to \R$, such that $g(y) \sim h(y)$ as $y \to \infty$
\begin{equation}\label{eq:concentration_h_sim_rho}
	\int_0^\infty g(y) \rho(y,k_n) \alpha e^{-\alpha y^\prime} \dd y^\prime \sim  
		2\alpha \xi^{2\alpha} h(2\log(k_n/\xi)) k_n^{-(2\alpha + 1)},
\end{equation}
as $n \to \infty$.
\end{corollary}

@@

%For any positive sequence $a_n \to \infty$ and $C > 0$ we define
%\begin{equation}\label{eq:def_K_C_set}
%	\Kcal_C(a_n) = \left\{y \in \R_+ : \frac{a_n - C \sqrt{a_n \log(a_n)}}{\xi} \vee 1 \le e^{\frac{y}{2}}
%	\le \frac{a_n + C \sqrt{a_n \log(a_n)}}{\xi} \right\}.
%\end{equation}
%In addition we define
%\begin{equation}\label{eq:def_K_C_n_set}
%	\Kcal_{C,n}(a_n) := (-I_n, I_n] \times ((0,R_n] \cap \Kcal_{C}(a_n)),
%\end{equation}
%where $I_n := \frac{\pi}{2}e^{R_n/2}$. Recall that $\Rcal = (-I_n, I_n] \times [0,R]$. 
The following corollary allows us to bound integrals of function by considering there maximum of $\Kcal_{C}(k_n)$.

@@

\begin{remark}[Concentration of heights argument]\label{rmk:concentration_argument}
%\TM{ again, this is a loaded term. I would in the very least change to ``concentration of height'' everywhere }
All the above corollaries use the same reasoning, namely that when the integrand contains $h_n(y) \rho(y,k_n)$, for some "nice" functions $h_n(y)$, then the main contribution is determined by the integration over $\Kcal_{C}(k_n)$.  This implies, for instance, that we only need to carefully analyze the functions $h_n(y)$ on $\Kcal_{C}(y)$, while for a certain class of functions we can even simply replace it with $h_n(2\log(k_n/\xi))$. We will refer collectively to any of these arguments as a \emph{concentration of heights argument}. For example, suppose we know that $h_n(y) = \Omega(1)$ and $h_n(y) = \bigO{k_n^4} e^{\alpha/2 y}$, while $h_n(y) = (1 + \smallO{1}) k_n^2 e^{\alpha/2 y}$, uniformly on $\Kcal_{C}(k_n)$. Then by a concentration of heights argument (in this case Corollary~\ref{cor:concentration_heights_asymptotics_n})
\begin{align*}
	\int_{\Rcal} h_n(y) \rho(y,k_n) f(x,y) \dd x \dd y 
	&= (1 + \smallO{1}) 2 \alpha \xi^{2\alpha} \, n \, k_n^2 (k_n/\xi)^{\alpha/2} k_n^{-(2\alpha + 1)} \\
	&= (1 + \smallO{1}) 2\alpha \xi^{5\alpha/2} \, n \, k_n^{1 + 5\alpha/2}.
\end{align*}
\end{remark}

@@

\begin{lemma}\label{lem:concentration_argument_rho_approximation}
Let $\alpha > \frac{1}{2}, \nu > 0$ and $k_n \to \infty$ such that $k_n = \smallO{n}$, $\ell_n = (1 + \epsilon_n)k_n$, with $\epsilon_n \to 0$ and define
\[
	\lambda_n^\pm = (\ell_n \pm C \sqrt{\ell_n \log(\ell_n)}) \wedge \xi, \quad \text{and} \quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi}\right).
\] 
In addition, let $\hat{\rho}_n(y,k) = \Prob{\Po(\hat{\mu}_n(y)) = k}$, with $\hat{\mu}_n(y) = (1 + \phi_n(y))\mu(y)$ and 
where $\phi_n(y)$ is a differentiable function satisfying:
\begin{enumerate}[\upshape i)]
\item For some $0 < \varepsilon < 1$, $\displaystyle \lim_{n \to \infty} \sup_{0 \le y \le (1 - \varepsilon)R_n} |\phi_n(y)| = 0$,
\item $\displaystyle \lim_{n \to \infty}  \sup_{y \in \Kcal_{C}(\ell_n)} |\phi_n^\prime(y)| = 0.$
\end{enumerate}
Then the following holds:
\begin{enumerate}
\item For any continuous function $h : \R_+ \rightarrow  \R$, such that $h(y) = \bigO{e^{\beta y}}$ as $y \to \infty$ for some $\beta < \alpha$, 
\begin{equation}\label{eq:error_bound_int_rho_approx_not_K}
	\int_{\R_+ \setminus (a_n^-, a_n^+)} \hat{\rho}_n(y,k_n) h(y) \alpha e^{-\alpha y} \dd y
	= \bigO{k_n^{-(1+C^2)/2}},
\end{equation}
as $n \to \infty$.
\item If in addition, $h(a_n) \sim h(b_n)$ whenever $a_n \sim b_n$, as $n \to \infty$, then,
\begin{equation}\label{eq:concentration_h_rho_approx}
	\int_0^\infty h(y) \hat{\rho}_n(y,k_n) \alpha e^{-\alpha y} \dd y \sim  
		\int_0^\infty h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y,
\end{equation}
as $n \to \infty$.
\end{enumerate}
\end{lemma}

@@

Since $h(y) = \bigO{e^{\beta y}}$ we have
\begin{align*}
	\int_{(1-\varepsilon^\prime)R_n}^{R_n} h(y) \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
	&= \bigO{1} \hat{\rho}_n((1-\varepsilon^\prime)R,k_n) e^{-(\alpha-\beta)(1-\varepsilon^\prime)R} \\
	&= \bigO{\hat{\rho}_n((1-\varepsilon^\prime)R,k_n) n^{-2(\beta-\alpha)(1-\varepsilon^\prime)}}.
\end{align*}
By assumption on $\hat{\mu}_n(y)$ we have that $\hat{\mu}_n((1-\varepsilon^\prime)R) = \bigT{\mu((1-\varepsilon^\prime)R} = \bigT{n^{2(1-\varepsilon^\prime)}}$. Since $k_n = \smallO{n}$, by our choice of $\varepsilon^\prime$, $\hat{\mu}_n((1-\varepsilon^\prime)R)/k_n = \omega\left(n^{1 - 2\varepsilon^\prime}\right) \to \infty$ as $n \to \infty$. We can now use Stirling's approximation to bound $\hat{\rho}_n((1-\varepsilon^\prime)R,k_n)$ as
\begin{align*}
	\hat{\rho}_n((1-\varepsilon^\prime)R,k_n) &= \Prob{\Po(\hat{\mu}_n((1-\varepsilon^\prime)R)) = k_n} \\
	&= \frac{\hat{\mu}_n((1-\varepsilon^\prime)R)^{k_n}}{k_n!} e^{-\hat{\mu}_n((1-\varepsilon^\prime)R)}\\
	&= \bigO{1} k_n^{-1/2} \left(\frac{\hat{\mu}_n((1-\varepsilon^\prime)R)}{k_n}\right)^{k_n} e^{k_n - \hat{\mu}_n((1-\varepsilon^\prime)R)}\\
	&= \bigO{1} k_n^{-1/2} e^{k_n\left(1 - \frac{\hat{\mu}_n((1-\varepsilon^\prime)R)}{k_n}\right)+ \log\left(\frac{\hat{\mu}_n((1-\varepsilon^\prime)R)}{k_n}\right)}\\
	&\le \bigO{1} k_n^{-1/2} e^{-\hat{\mu}_n((1-\varepsilon^\prime)R)/2},
\end{align*}
where the last line follows since $1 - x + \log(x) \le -x/2$ for large enough $x$. We conclude that
\[
	\int_{(1-\varepsilon^\prime)R_n}^{R_n} h(y) \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
	= \bigO{k_n^{-1/2} n^{-2(\beta-\alpha)(1-\varepsilon^\prime)} e^{-n^{2(1-\varepsilon^\prime)}}}
	= \bigO{k_n^{(1+C^2)/2}}.
\]

We are left to show that for sufficiently large $C > 0$,
\begin{equation}\label{eq:concentration_argument_an_-}
	 \int_0^{a_n^-} \hat{\rho}_n(y,k_n) e^{(\beta-\alpha) y} \dd y = \bigO{k_n^{-(1+C^2)/2}},
\end{equation}
and
\begin{equation}\label{eq:concentration_argument_an_+}
	\int_{a_n^+}^{(1-\varepsilon^\prime)R_n} \hat{\rho}_n(y,k_n) e^{(\beta-\alpha) y} \dd y = \bigO{k_n^{-(1+C^2)/2}}.
\end{equation}
%\TM{ Why can we change the upper limit of the integral? PLease elaborate (in the paper) }

For simplicity we write $\mu(y) := \mu\left(\BallPo{y}\right)$. Now fix some $0 < \delta < 1$ and let $n$ be large enough such that 
\[
\sup_{0 < y \le (1-\varepsilon^\prime)R_n} |\phi_n(y)| < \delta, \quad
\lambda_n^+(1 - \delta) > k_n \quad \text{and} \quad
\lambda_n^-(1 + \delta) < k_n.
\]

>>>>

Here we show that if we integrate with respect to the function $\hat{\rho}_n(y,k_n) = \Prob{\Po(\mu_n(y)) = k_n}$ then we may restrict integration with respect to the \emph{height} $y$ to an interval on which $\mu_n(y) = \bigT{k_n}$. We will refer to such a result as a \emph{concentration of heights} result. In addition, if $\mu_n(y)$ is equivalent to $\mu(y)$ on this interval, then we may replace $\hat{\rho}_n(y,k_n)$ in the integral with $\rho(y,k_n) = \Prob{\Po(\mu(y)) = k_n}$ (the degree distribution of the typical point in $\Ginf$).

@@

\begin{lemma}\label{lem:concentration_argument}
Let $\alpha > \frac{1}{2}$, $\nu > 0$, $(k_n)_{n \ge 1}$ be any positive sequence such that $k_n \to \infty$ and $k_n = \smallO{n}$ and let $\ell_n = k_n(1 + \epsilon_n)$, with $\epsilon_n \to 0$. In addition, define for any constant $C > 0$,
\[
	\lambda_n^\pm = (\ell_n \pm C \sqrt{\ell_n \log(\ell_n)}) \wedge \xi, 
	\quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi}\right).
\] 
Then the following holds.
\begin{enumerate}
\item For any continuous function $h : \R_+ \rightarrow  \R$, such that $h(y) = \bigO{e^{\beta y}}$ as $y \to \infty$ for some $\beta < \alpha$, 
\begin{equation}\label{eq:error_bound_int_rho_not_K}
	\int_{\R_+ \setminus (a_n^-, a_n^+)} \rho(y,k_n) h(y) \alpha e^{-\alpha y} \dd y
	= \bigO{k_n^{-(1+C^2)/2}},
\end{equation}
as $n \to \infty$.
\item If in addition $C > \sqrt{4\alpha + 1}$ and $h(a_n) \sim h(b_n)$ whenever $a_n \sim b_n$, as $n \to \infty$. Then, 
\begin{equation}\label{eq:concentration_h_rho}
	\int_0^\infty h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y \sim  
		2\alpha \xi^{2\alpha} h(2\log(k_n/\xi)) k_n^{-(2\alpha + 1)},
\end{equation}
as $n \to \infty$.
\end{enumerate}
\end{lemma}

@@

\paragraph{Proof of the first statement.}
Recall (see proof of Proposition~\ref{prop:asymp}) that $\rho(y,k_n)$, as a function of $y$, is strictly increasing on $[0,a_n^-]$ and strictly decreasing on $[a_n^+,\infty)$. Therefore, by our assumption on $h(y)$,
\begin{align*}
	&\hspace{-20pt}\int_{\R_+ \setminus (a_n^-, a_n^+)} h(y) \rho(y,k_n) 
		\alpha e^{-\alpha y} \dd y\\
    &= \bigO{1} \int_0^{a_n^-} e^{\beta y} \rho(y,k_n) \alpha e^{-\alpha y} \dd y 
    	+ \bigO{1}\int_{a_n^+}^{\infty} e^{\beta y} \rho(y,k_n) \alpha e^{-\alpha y} \dd y \\
    &= \bigO{1} \int_0^{a_n^-} \rho(y,k_n) e^{-(\alpha-\beta) y} \dd y 
   		+ \bigO{1} \int_{a_n^+}^{\infty} \rho(y,k_n) e^{-(\alpha-\beta) y} \dd y\\
   	&\le \bigO{1}\rho(a_n^-,k_n)\int_0^{a_n^-} e^{-(\alpha-\beta) y} \, \dd y
   		+ \bigO{1} \rho(a_n^+,k_n) \int_{a_n^+}^{\infty} e^{-(\alpha-\beta) y} \, \dd y.
\end{align*}
Since $\alpha - \beta > 0$, we conclude that
\begin{equation}\label{eq:concentration_lemma_integral_bound}
	\int_{\R_+ \setminus (a_n^-, a_n^+)} h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y
	= \bigO{1} \left(\rho(a_n^-,k_n) + \rho(a_n^+,k_n)\right).
\end{equation}

We shall now bound the terms $\rho(a_n^\pm,k_n)$. We explicitly show the bound for $\rho(a_n^+,k_n)$, the computation for $\rho(a_n^-,k_n)$ is similar. Using Stirling's approximation $k! \sim \sqrt{2\pi} k^{k + 1/2} e^{-k}$ as $k \to \infty$ we write
\begin{align*}
	\rho(a_n^+,k_n) &= \frac{\mu(a_n^+)^{k_n}}{k_n!} e^{-\mu(a_n^+)} \\
	&\sim (2\pi)^{-1/2} k_n^{-1/2} \left(\frac{\mu(a_n^+)}{k_n}\right)^{k_n} e^{-(\mu(a_n^+) - k_n)}\\
	&= (2\pi)^{-1/2} k_n^{-1/2} 
		e^{-k_n\left(\frac{\mu(a_n^+)}{k_n} - 1 - \log\left(\frac{\mu(a_n^+)}{k_n}\right)\right)}.
\end{align*}

@@

\paragraph{Proof of the second statement.} By the mean value theorem for definite integrals, there exists a $c_n \in (a_n^-, a_n^+)$ such that
\[
	\int_{a_n^-}^{a_n^+} h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y
	= h(c_n) \int_{a_n^+}^{a_n^+} \rho(y,k_n) \alpha e^{-\alpha y} \dd y.
\]
Since $\int_0^\infty \rho(y,k_n) \alpha e^{-\alpha y} \dd y = \bigT{k_n^{-(2\alpha + 1)}}$, taking any $C > \sqrt{4\alpha + 1}$, \eqref{eq:error_bound_int_rho_not_K} implies that
\[
	\int_{a_n^+}^{a_n^+} \rho(y,k_n) \alpha e^{-\alpha y} \dd y
	= (1 + \smallO{1})\int_0^\infty \rho(y,k_n) \alpha e^{-\alpha y} \dd y,
\]
from which we conclude that (see~\eqref{eq:degree_distribution_P_asymptotics}),
\[
	\int_{a_n^+}^{a_n^+} \rho(y,k_n) \alpha e^{-\alpha y} \dd y = (1 + \smallO{1}) 2\alpha \xi^{2\alpha} k_n^{-(2\alpha + 1)},
\]
as $n \to \infty$. Finally, since $c_n \in (a_n^-, a_n^+)$ it follows that
\[
	\left|\frac{c_n}{2\log(k_n/\xi)} - 1\right| \le 2 C \sqrt{\frac{\log(k_n)}{k_n}}, 
\]
so that $c_n \sim 2\log(k_n/\xi)$. Therefore, by assumption on $h$ 
\[
	\int_{a_n^-}^{a_n^+} h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y
	\sim h(c_n) 2\alpha \xi^{2\alpha} k_n^{-(2\alpha + 1)} 
	\sim 2\alpha \xi^{2\alpha} h(2\log(k_n/\xi)) k_n^{-(2\alpha + 1),}
\]
as $n \to \infty$.
\end{proof}

@@

\begin{corollary}\label{cor:concentration_of_heights_asymptotics}
Let $h : \R_+ \to \R$ be any continuous function such that for some $\beta < \alpha$, $h(y) = \bigO{e^{\beta y}}$ as $y \to \infty$ and $h(a_n) \sim h(b_n)$ whenever $a_n \sim b_n$. Then for any other continuous function $g: \R_+ \to \R$, such that $g(y) \sim h(y)$ as $y \to \infty$
\begin{equation}\label{eq:concentration_h_sim_rho}
	\int_0^\infty g(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y \sim  
		2\alpha \xi^{2\alpha} h(2\log(k_n/\xi)) k_n^{-(2\alpha + 1)},
\end{equation}
as $n \to \infty$.
\end{corollary}

@@

For any $C > 0$ we define
\begin{equation}\label{eq:def_K_C_set}
	\Kcal_C(k_n) = \left\{y \in \R_+ : \frac{k_n - C \sqrt{a_n \log(k_n)}}{\xi} \vee 1 \le e^{\frac{y}{2}}
	\le \frac{k_n + C \sqrt{k_n \log(k_n)}}{\xi} \right\}.
\end{equation}
%In addition we define
%\begin{equation}\label{eq:def_K_C_n_set}
%	\Kcal_{C,n}(a_n) := (-I_n, I_n] \times ((0,R] \cap \Kcal_{C}(a_n)),
%\end{equation}
%where $I_n := \frac{\pi}{2}e^{R/2}$. Recall that $\Rcal = (-I_n, I_n] \times [0,R]$. 
The following corollary allows us to bound integrals of functions $h_n(y)$ by considering their maximum of $\Kcal_{C}(k_n)$.

@@

\begin{remark}[Concentration of heights argument]\label{rmk:concentration_argument}
%\TM{ again, this is a loaded term. I would in the very least change to ``concentration of height'' everywhere }
All the above corollaries use the same reasoning, namely that when the integrand contains $h_n(y) \rho(y,k_n)$, for some "nice" functions $h_n(y)$, then the main contribution is determined by the integration over $\Kcal_{C}(k_n)$.  This implies, for instance, that we only need to carefully analyze the functions $h_n(y)$ on $\Kcal_{C}(y)$, while for a certain class of functions we can even simply replace it with $h_n(2\log(k_n/\xi))$. We will refer collectively to any of these arguments as a \emph{concentration of heights argument}. For example, suppose we know that $h_n(y) = \Omega(1)$ and we can obtain some general crude bound $h_n(y) = \bigO{k_n^s} e^{\alpha/2 y}$ for some $s > 0$ for $y \in \R_+$. Then, if we can obtain a more precise bound $h_n(y) = (1 + \smallO{1}) k_n^2 e^{\alpha/2 y}$ uniformly on $\Kcal_{C}(k_n)$, by a concentration of heights argument (in this case Corollary~\ref{cor:concentration_heights_asymptotics_n})
\begin{align*}
	\int_{\Rcal} h_n(y) \rho(y,k_n) f(x,y) \dd x \dd y 
	&= (1 + \smallO{1}) 2 \alpha \xi^{2\alpha} \, n \, k_n^2 (k_n/\xi)^{\alpha/2} k_n^{-(2\alpha + 1)} \\
	&= (1 + \smallO{1}) 2\alpha \xi^{5\alpha/2} \, n \, k_n^{1 + 5\alpha/2}.
\end{align*}
\end{remark}

@@

\begin{lemma}\label{lem:concentration_argument_rho_approximation}
Let $\alpha > \frac{1}{2}, \nu > 0$ and $k_n \to \infty$ such that $k_n = \smallO{n}$, $\ell_n = (1 + \epsilon_n)k_n$, with $\epsilon_n \to 0$ and define
\[
	\lambda_n^\pm = (\ell_n \pm C \sqrt{\ell_n \log(\ell_n)}) \wedge \xi, \quad \text{and} \quad a_n^\pm = 2 \log\left(\frac{\lambda_n^\pm}{\xi}\right).
\] 
In addition, let $\hat{\rho}_n(y,k) = \Prob{\Po(\hat{\mu}_n(y)) = k}$, with $\hat{\mu}_n(y) = (1 + \phi_n(y))\mu(y)$ and 
where $\phi_n(y)$ is a differentiable function satisfying:
\begin{enumerate}[\upshape i)]
\item For some $0 < \varepsilon < 1$, $\displaystyle \lim_{n \to \infty} \sup_{0 \le y \le (1 - \varepsilon)R} |\phi_n(y)| = 0$,
\item $\displaystyle \lim_{n \to \infty}  \sup_{y \in \Kcal_{C}(\ell_n)} |\phi_n^\prime(y)| = 0.$
\end{enumerate}
Then the following holds:
\begin{enumerate}
\item For any continuous function $h : \R_+ \rightarrow  \R$, such that $h(y) = \bigO{e^{\beta y}}$ as $y \to \infty$ for some $\beta < \alpha$, 
\begin{equation}\label{eq:error_bound_int_rho_approx_not_K}
	\int_{\R_+ \setminus (a_n^-, a_n^+)} \hat{\rho}_n(y,k_n) h(y) \alpha e^{-\alpha y} \dd y
	= \bigO{k_n^{-(1+C^2)/2}},
\end{equation}
as $n \to \infty$.
\item If in addition, $h(a_n) \sim h(b_n)$ whenever $a_n \sim b_n$, as $n \to \infty$, then,
\begin{equation}\label{eq:concentration_h_rho_approx}
	\int_0^\infty h(y) \hat{\rho}_n(y,k_n) \alpha e^{-\alpha y} \dd y \sim  
		\int_0^\infty h(y) \rho(y,k_n) \alpha e^{-\alpha y} \dd y,
\end{equation}
as $n \to \infty$.
\end{enumerate}
\end{lemma}

@@

Since $h(y) = \bigO{e^{\beta y}}$ we have
\begin{align*}
	\int_{(1-\varepsilon^\prime)R}^{R} h(y) \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
	&= \bigO{1} \hat{\rho}_n((1-\varepsilon^\prime)R,k_n) e^{-(\alpha-\beta)(1-\varepsilon^\prime)R} \\
	&= \bigO{\hat{\rho}_n((1-\varepsilon^\prime)R,k_n) n^{-2(\beta-\alpha)(1-\varepsilon^\prime)}}.
\end{align*}
By assumption on $\hat{\mu}_n(y)$ we have that $\hat{\mu}_n((1-\varepsilon^\prime)R) = \bigT{\mu((1-\varepsilon^\prime)R} = \bigT{n^{2(1-\varepsilon^\prime)}}$. Since $k_n = \smallO{n}$, by our choice of $\varepsilon^\prime$, $\hat{\mu}_n((1-\varepsilon^\prime)R)/k_n = \omega\left(n^{1 - 2\varepsilon^\prime}\right) \to \infty$ as $n \to \infty$. We can now use Stirling's approximation to bound $\hat{\rho}_n((1-\varepsilon^\prime)R,k_n)$ as
\begin{align*}
	\hat{\rho}_n((1-\varepsilon^\prime)R,k_n) &= \Prob{\Po(\hat{\mu}_n((1-\varepsilon^\prime)R)) = k_n} \\
	&= \frac{\hat{\mu}_n((1-\varepsilon^\prime)R)^{k_n}}{k_n!} e^{-\hat{\mu}_n((1-\varepsilon^\prime)R)}\\
	&= \bigO{1} k_n^{-1/2} \left(\frac{\hat{\mu}_n((1-\varepsilon^\prime)R)}{k_n}\right)^{k_n} e^{k_n - \hat{\mu}_n((1-\varepsilon^\prime)R)}\\
	&= \bigO{1} k_n^{-1/2} e^{k_n\left(1 - \frac{\hat{\mu}_n((1-\varepsilon^\prime)R)}{k_n}\right)+ \log\left(\frac{\hat{\mu}_n((1-\varepsilon^\prime)R)}{k_n}\right)}\\
	&\le \bigO{1} k_n^{-1/2} e^{-\hat{\mu}_n((1-\varepsilon^\prime)R)/2},
\end{align*}
where the last line follows since $1 - x + \log(x) \le -x/2$ for large enough $x$. We conclude that
\[
	\int_{(1-\varepsilon^\prime)R}^{R} h(y) \hat{\rho}_n(y,k_n) e^{-\alpha y} \dd y
	= \bigO{k_n^{-1/2} n^{-2(\beta-\alpha)(1-\varepsilon^\prime)} e^{-n^{2(1-\varepsilon^\prime)}}}
	= \bigO{k_n^{(1+C^2)/2}}.
\]

We are left to show that for sufficiently large $C > 0$,
\begin{equation}\label{eq:concentration_argument_an_-}
	 \int_0^{a_n^-} \hat{\rho}_n(y,k_n) e^{(\beta-\alpha) y} \dd y = \bigO{k_n^{-(1+C^2)/2}},
\end{equation}
and
\begin{equation}\label{eq:concentration_argument_an_+}
	\int_{a_n^+}^{(1-\varepsilon^\prime)R} \hat{\rho}_n(y,k_n) e^{(\beta-\alpha) y} \dd y = \bigO{k_n^{-(1+C^2)/2}}.
\end{equation}
%\TM{ Why can we change the upper limit of the integral? PLease elaborate (in the paper) }

For simplicity we write $\mu(y) := \mu\left(\BallPo{y}\right)$. Now fix some $0 < \delta < 1$ and let $n$ be large enough such that 
\[
\sup_{0 < y \le (1-\varepsilon^\prime)R} |\phi_n(y)| < \delta, \quad
\lambda_n^+(1 - \delta) > k_n \quad \text{and} \quad
\lambda_n^-(1 + \delta) < k_n.
\]

Next, recall that the function $\lambda \mapsto \Prob{\Po(\lambda) = k}$ is monotonic increasing on $[0,k]$ and monotonic decreasing on $[k, \infty)$. Then since for $n$ large enough we have 
\[
	\hat{\mu}_n(y) = \mu(y)(1 + \phi_n(y)) \ge \mu(y)(1 - \delta) \ge \mu(a_n^+)(1 - \delta)
	= (\ell_n + C \kappa_n)(1 - \delta) > k_n,
\]
it follows that 
\[
	\hat{\rho}_n(y,k_n) = \Prob{\Po(\hat{\mu}_n(y)) = k_n} \le \Prob{\Po(\mu(y)(1-\delta)) = k_n},
\]
for all $a_n^+ \le y \le (1-\varepsilon^\prime)R$. By making the change of variables $z = \mu^{-1}(\mu(y)(1-\delta)) = y + 2 \log(1-\delta)$ we then get
\begin{align*}
	\int_{a_n^+}^{(1-\varepsilon^\prime)R} \hat{\rho}_n(y,k_n) e^{(\beta - \alpha)y} \dd y
	&\le \int_{a_n^+}^{(1-\varepsilon^\prime)R} \Prob{\Po(\mu(y)(1-\delta)) = k_n} 
		e^{(\beta-\alpha) y} \dd y\\
	&= (1-\delta)^{\beta - \alpha} \int_{a_n^+ + 2\log(1-\delta)}^{(1-\varepsilon^\prime)R + 2\log(1-\delta)} 
		\Prob{\Po(\mu(z)) = k_n} e^{(\beta - \alpha)z} \dd z\\
	&= \bigO{1} \int_{a_n^+}^{\infty} \rho(z,k_n) e^{(\beta - \alpha)z} \dd z\\
	&= \bigO{k_n^{-(1+C^2)/2}},
\end{align*}
where the last line is due to Lemma~\ref{lem:concentration_argument}. This proves~\eqref{eq:concentration_argument_an_+}.
